Convex optimisation in communications with cvxpy

### 2017-07-17 article_cvxpy.tex
Shortened version for review

\section{Example: power minimisation in communications}
For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2D$ Euclidian space. Each of the transmitters has power $p_i$. How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers? This question is relevant to a telecoms company who want to offer a service at a minimum quality standard. We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and maximum power value that any transmitter can reach $P_{\text{max}}$:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
&\text{subject to} \quad &&p_j \leq P_{\max}\\
& \quad &&p_j \geq 0\\
& \quad &&\gamma_i \geq \gamma_0&&
\end{align*}
where symbols $\succ$, $\succeq$ denote element-wise inequalities between vectors or matrices.

>>>>

\section{Example: power minimisation in communications}
For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2$D Euclidian space. Each of the transmitters has power $p_i$. How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers? This question is relevant to a telecoms company who want to offer a service at a minimum quality standard. We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and maximum power value that any transmitter can reach $P_{\text{max}}$:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
&\text{subject to} \quad &&p_j \leq P_{\max}\\
& \quad &&p_j \geq 0\\
& \quad &&\gamma_i \geq \gamma_0&&
\end{align*}
where symbols $\succ$, $\succeq$ denote element-wise inequalities between vectors or matrices.
